\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/experiment.tex
experiment figure

\begin{table*}[t]
	\centering
	\begin{tabular}{|c|c|c|c|c|}
		\hline
		\textbf{Category}  & \textbf{Application} & \textbf{Leaked Sensitive Information}                      \\
		\hline
		Finance App         & Alipay      & Alipay account, personal assets (blance)          \\
		\hline
		Social  Finance App & WeChat      & WeChat account, , chat history             \\
		\hline
		Social App          & QQ          & QQ account, interpersonal nexus, chat history    \\
		\hline
		Social App          & Twitter     & Twitter account, interpersonal nexus             \\
		\hline
		Social App          & Gmail       & Gmail account, mail records                      \\
		\hline
		Finance App         & ICBC        & ICBC account, password, personal assets (balance)  \\
		\hline
		Finance App         & Paypal      & Paypal account, balance, bank accounts            \\
		\hline
		Tool                & Chrome      & Sites visited                                    \\
		\hline
		Tool                & Health      & personal physical metrics      					 \\
		\hline
	\end{tabular}
	\linebreak
	\caption{Information Extraction via Manual Analysis.}\shuqing{Compress.}
	\label{table:information_extracted}
\end{table*}

>>>>

\begin{table*}[t]
	\centering
	\begin{tabular}{|c|c|c|c|c|c|c|} 
		\hline
		\textbf{Keyword}                               & Account & Password & Phone number & Email & Username & Regexp for email~  \\ 
		\hline
		\textbf{Number of records containing keywords} & 680     & 1596     & 1510         & 164   & 522      & 78                 \\
		\hline
	\end{tabular}
	\linebreak
	\caption{Information Extraction via Manual Analysis.}
	\label{table:information_extracted}
\end{table*}
